
---
title: "OM Data Downweighting Report"
subtitle: "ABT-MSE"
author: "Tom Carruthers"
date:  "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true 
---


<style type="text/css">

body{ /* Normal  */
   font-size: 16px;
}
td {  /* Table  */
   font-size: 14px;
}
title { /* title */
 font-size: 26px;
}
h1 { /* Header 1 */
 font-size: 24px;
 color: DarkBlue;
}
h2 { /* Header 2 */
 font-size: 21px;
 color: DarkBlue;
}
h3 { /* Header 3 */
 font-size: 19px;
 color: DarkBlue;
}
code.r{ /* Code block */
  font-size: 16px;
}
pre { /* Code block */
  font-size: 16px
}
</style>

# Introduction / notes

This is a short document intended to illustrate sensitivity of core operating model estimates to downweighting various data types .



# Comparison of global likelihoods

```{r loadsecret,echo=F,warning=F,error=F,message=F}

outs<-OMIs<-new('list')
nOMs<-length(OMdirs)

sfInit(parallel=T,cpus=8)
M3read<-ABTMSE::M3read
sfExport("M3read")

outread<-function(x,OMdirs)M3read(OMdirs[x])
OMIread<-function(x,OMdirs){
  load(paste0(OMdirs[x],"/OMI"))
  return(OMI)
}

outs<-sfLapply(1:nOMs,outread,OMdirs=OMdirs)
OMIs<-sfLapply(1:nOMs,OMIread,OMdirs=OMdirs)
#Snams<-c("East_I","West_I","SOO","SOO_MC", "ETag")

LHs<-data.frame(array(NA,c(nOMs,18)))
names(LHs)<- c("OM","Code","Cat", "CR", "Surv", "Comp", "SOO", "Tag", "Rec", "Mov", "Sel", "SRA", "SSB", "Dep",  "MI","R0dif","TOT","TOTn")


for(i in 1:nOMs){
  LHs[i,1]<-OMIs[[i]]@Name
  LHs[i,2]<-OMcode
  #wts<-OMIs[[i]]@LHw[c(1:6,8:15)]
  LHs[i,3:17]<-outs[[i]]$obj[1:15]
  LHs[i,is.na(LHs[i,])|LHs[i,]=='Inf']<-0
  LHs[i,3:17]<-round(LHs[i,3:17],1)
  LHs[i,17]<-outs[[i]]$obj[15]
  #LHs[i,18]<-LHs[i,16]-sum(LHs[i,13:15])
  LHs[i,18]<-LHs[i,17]-sum(LHs[i,9:16])
}

colr<-function(x,ncol=1000,cond=NA){
  if(sd(x)==0){
    tempcol=rep('black',length(x))
  }else{  
  if(!is.na(cond[1]))x[cond]<-mean(x[!cond])
  xconv<-1-((x-min(x,na.rm=T))/(max(x,na.rm=T)-min(x,na.rm=T)))
  tempcol<-hsv(h=xconv*0.33)
  if(!is.na(cond[1]))tempcol[cond]="black"
  }
  tempcol
}

LHs<-LHs[,c(1:12,15:18)]

for(i in 3:16)LHs[,i]<-round(LHs[,i],1)
  
library(dplyr)
library(kableExtra)

```


These are weighted negative log-likelihoods. Color coding is by column. Rows with all black values depict models that did not converge. 

```{r TotLHF, fig.width=11, fig.height=9,echo=FALSE}

LHs%>%
  mutate(
    OM=cell_spec(OM,"html",bold=T),
    Code=cell_spec(Code,"html",bold=T),
    Cat=cell_spec(Cat,"html",color=colr(LHs$Cat),bold=T),
    CR=cell_spec(CR,"html",color=colr(LHs$CR),bold=T),
    Surv=cell_spec(Surv,"html",color=colr(LHs$Surv),bold=T),
    Comp=cell_spec(Comp,"html",color=colr(LHs$Comp),bold=T),
    SOO=cell_spec(SOO,"html",color=colr(LHs$SOO),bold=T),
    Tag=cell_spec(Tag,"html",color=colr(LHs$Tag),bold=T),
    Rec=cell_spec(Rec,"html",color=colr(LHs$Rec),bold=T),
    Mov=cell_spec(Mov,"html",color=colr(LHs$Mov),bold=T),
    Sel=cell_spec(Sel,"html",color=colr(LHs$Sel),bold=T),
    SRA=cell_spec(SRA,"html",color=colr(LHs$SRA),bold=T),
    MI=cell_spec(MI,"html",color=colr(LHs$MI),bold=T),
    R0dif=cell_spec(R0dif,"html",color=colr(LHs$R0dif),bold=T),
    TOT=cell_spec(TOT,"html",color=colr(LHs$TOT),bold=T),
    TOTn=cell_spec(TOTn,"html",color=colr(LHs$TOTn),bold=T)

  )%>%
  select(OM, Code,Cat,CR,Surv,Comp,SOO,Tag,Rec,Mov,Sel,SRA,MI,R0dif,TOT,TOTn) %>%
  kable(format = "html", escape = F) %>%
  kable_styling("striped")#, full_width = T) 


```
Cat = catch data by fleet, quarter and area. CR = the fishery dependent catch rate (CPUE) indices, Surv = fishery-independent survey indices, Comp = length composition data, SOO = stock of origin data, ET = Electronic tagging data, Rec = prior on recruitment deviations, Mov = prior on movement parameters, Sel = prior on size selectivity parameters, SRA = penalty incurred when catches exceed F=1 catches in the stock reduction analysis phase (1864-1964), MI = a prior on similarity to the 'Master Index' that predicts F by year, area, season and fleet, R0dif = a prior on the difference in R0 estimated in two-phase recruitment models (recruitment level 1 and 3), TOT = total global objective function, TOTn = total global objective function without priors.  


These are weighted negative log-likelihoods expressed as differences from the base-case weighting. Color coding is by column. Rows with all black values depict models that did not converge. 


```{r TotLHFconv, fig.width=9, fig.height=9,echo=FALSE}


for(i in 3:16)LHs[,i]<-round(LHs[,i]-LHs[1,i],1)

LHs%>%
  mutate(
    OM=cell_spec(OM,"html",bold=T),
    Code=cell_spec(Code,"html",bold=T),
    Cat=cell_spec(Cat,"html",color=colr(LHs$Cat),bold=T),
    CR=cell_spec(CR,"html",color=colr(LHs$CR),bold=T),
    Surv=cell_spec(Surv,"html",color=colr(LHs$Surv),bold=T),
    Comp=cell_spec(Comp,"html",color=colr(LHs$Comp),bold=T),
    SOO=cell_spec(SOO,"html",color=colr(LHs$SOO),bold=T),
    Tag=cell_spec(Tag,"html",color=colr(LHs$Tag),bold=T),
    Rec=cell_spec(Rec,"html",color=colr(LHs$Rec),bold=T),
    Mov=cell_spec(Mov,"html",color=colr(LHs$Mov),bold=T),
    Sel=cell_spec(Sel,"html",color=colr(LHs$Sel),bold=T),
    SRA=cell_spec(SRA,"html",color=colr(LHs$SRA),bold=T),
    MI=cell_spec(MI,"html",color=colr(LHs$MI),bold=T),
    R0dif=cell_spec(R0dif,"html",color=colr(LHs$R0dif),bold=T),
    TOT=cell_spec(TOT,"html",color=colr(LHs$TOT),bold=T),
    TOTn=cell_spec(TOTn,"html",color=colr(LHs$TOTn),bold=T)

  )%>%
  select(OM, Code,Cat,CR,Surv,Comp,SOO,Tag,Rec,Mov,Sel,SRA,MI,R0dif,TOT,TOTn) %>%
  kable(format = "html", escape = F) %>%
  kable_styling("striped")#, full_width = T) 


```
Cat = catch data by fleet, quarter and area. CR = the fishery dependent catch rate (CPUE) indices, Surv = fishery-independent survey indices, Comp = length composition data, SOO = stock of origin data, ET = Electronic tagging data, Rec = prior on recruitment deviations, Mov = prior on movement parameters, Sel = prior on size selectivity parameters, SRA = penalty incurred when catches exceed F=1 catches in the stock reduction analysis phase (1864-1964), MI = a prior on similarity to the 'Master Index' that predicts F by year, area, season and fleet, R0dif = a prior on the difference in R0 estimated in two-phase recruitment models (recruitment level 1 and 3), TOT = total global objective function, TOTn = total global objective function without priors.  


# Comparison with 2017 Stock Assessments


```{r 2017comp, fig.width=8.5, fig.height=5,echo=FALSE}

ny<-outs[[1]]$ny
nHy<-outs[[1]]$nHy
np<-outs[[1]]$np
ns<-outs[[1]]$ns
nr<-outs[[1]]$nr
nf<-outs[[1]]$nf
nl<-outs[[1]]$nl
na<-outs[[1]]$na
cols<-c('black','blue','blue','orange','orange','grey')
ltys<-c(1,        1,      2,    1,          2,    1)
muSSB<-new('list')
ylim<-new('list')
ylim[[1]]<-ylim[[2]]<-c(0,-1000)

for(OM in 1:nOMs){
  Nind<-TEG(dim(outs[[OM]]$N))
  SSB<-array(NA,dim(outs[[OM]]$N))
  SSB[Nind]<-outs[[OM]]$N[Nind]*outs[[OM]]$mat_age[Nind[,c(1,4)]]*outs[[OM]]$wt_age[Nind[,c(2,4,1)]]
  SSBsum<-apply(SSB,c(2,3,5),sum) # SSB by year and area in spawning season
  SSBmu<-apply(SSBsum,c(1,3),mean)
  #sum(SSBmu[55,])==sum(SSBsum[55,,])/4 # Debug test
  muSSB[[OM]]<-array(NA,c(np,ny))
  muSSB[[OM]][1,]<-apply(SSBmu*rep(c(0,0,0,1,1,1,1),each=outs[[OM]]$ny),1,sum)
  muSSB[[OM]][2,]<-apply(SSBmu*rep(c(1,1,1,0,0,0,0),each=outs[[OM]]$ny),1,sum)
  snams<-c("East","West")
  stocknames<-c("East area","West area","All Atlantic")
  if(max(muSSB[[OM]][1,])>ylim[[1]][2])ylim[[1]][2]<-max(muSSB[[OM]][1,])
  if(max(muSSB[[OM]][2,])>ylim[[2]][2])ylim[[2]][2]<-max(muSSB[[OM]][2,])
}

yrs<-OMIs[[1]]@years[1]:OMIs[[1]]@years[2]
par(mfcol=c(1,2),mai=c(0.35,0.35,0.01,0.1),omi=c(0.4,0.4,0.4,0.05))

for(pp in np:1){
  
  # SSB 
  tdat<-subset(dat,dat$area==snams[pp])[,c(2:4)]
  names(tdat)<-c("Assessment","Year","Val")
  
  plot(yrs,muSSB[[1]][pp,]/1E6,lwd=2,ylab="",type="l",ylim=ylim[[pp]]/1E6,yaxs='i',col=cols[1],lty=ltys[1])
  for(i in 2:nOMs)lines(yrs,muSSB[[i]][pp,]/1E6,lwd=2,col=cols[i],lty=ltys[i])
  cond<-tdat$Assessment=="SS"
  lines(tdat$Year[cond],as.numeric(as.character(tdat$Val[cond]))/1000,col="#ff000090",lwd=2)
  lines(tdat$Year[!cond],as.numeric(as.character(tdat$Val[!cond]))/1000,col="#00ff0090",lwd=2)
  mtext(stocknames[pp],3,line=1,font=2)
  if(pp==np)mtext("SSB(kt)",2,line=2.8,font=2)
  
  if(pp==2)legend('top',legend=c(Snams,"SS","VPA"),cex=0.75,text.col=c(cols,'red','green'),lty=ltys,col=cols,text.font=2,bty='n')
  #if(pp==1)legend('top',legend=LHs[,1],cex=0.75,text.col=cols,lty=ltys,col=cols,text.font=2,bty='n')
}

mtext("Year",1,line=0.5,font=2,outer=T)



```

Figure 1. Regional spawning stock comparisons (by area, divisible by 45deg W) with 2017 stock assessment. Note that annual estimates from the operating model are calculated from average of the seasonal predictions. 



# Spawning Stock Biomass


```{r SSB, fig.width=8.5, fig.height=5,echo=FALSE}

F_E_E<-F_E_W<-F_W_E<-F_W_W<-F_EinW<-F_WinE<-SSB_W<-SSB_E<-D_W<-D_E<-new('list')
ind<-TEG(dim(outs[[1]]$N))
indw<-ind[,c(2,4,1)]

for(OM in 1:nOMs){
  
  B<-SSB<-array(NA,dim(outs[[OM]]$N))
 
  B[ind]<-outs[[OM]]$N[ind]*outs[[OM]]$wt_age[indw]
  SSB[Nind]<-outs[[OM]]$N[ind]*outs[[OM]]$mat_age[ind[,c(1,4)]]*outs[[OM]]$wt_age[ind[,c(2,4,1)]]
  
  #RAIp<-apply(B,c(5,3,2),sum) # r s y
  #muRAIp<-mean(RAIp)
  RAIpP<-apply(B,c(5,3,2,1),sum) # r s y p
  #RAIpP<-RAIpP/muRAIp
  #SSBpP<-apply(SSB,c(5,3,2,1),sum)# r s y p
    
  Wareas<-1:3
  Eareas<-4:7
  
  EinW<-apply(RAIpP[Wareas,,,1],3,sum)
  EinE<-apply(RAIpP[Eareas,,,1],3,sum)
  WinW<-apply(RAIpP[Wareas,,,2],3,sum)
  WinE<-apply(RAIpP[Eareas,,,2],3,sum)
  
  SSB_E[[OM]]<-apply(SSB[1,,2,,],1,sum)/1E6 #  y spawning season = 2
  SSB_W[[OM]]<-apply(SSB[2,,2,,],1,sum)/1E6 #  y spawning season = 2
 
  D_E[[OM]]<- SSB_E[[OM]]/SSB_E[[OM]][1]
  D_W[[OM]]<- SSB_W[[OM]]/SSB_W[[OM]][1]
  
  F_EinW[[OM]]<-EinW/(EinE+EinW)
  F_WinE[[OM]]<-WinE/(WinW+WinE)
  
  F_E_E[[OM]]<-EinE/(EinE+WinE)
  F_E_W[[OM]]<-EinW/(EinW+WinW)
  F_W_E[[OM]]<-WinE/(EinE+WinE)
  F_W_W[[OM]]<-WinW/(EinW+WinW)
 
}


ylim_SSB_W<-range(lapply(SSB_W,range))
ylim_SSB_E<-range(lapply(SSB_E,range))
ylim_D_W<-range(lapply(D_W,range))
ylim_D_E<-range(lapply(D_E,range))

par(mfrow=c(1,2),mai=c(0.35,0.35,0.4,0.01),omi=c(0.4,0.4,0.05,0.05))
yrs<-OMIs[[1]]@years[1]:OMIs[[1]]@years[2]

plot(yrs,SSB_W[[1]],col="white",ylim=c(0,ylim_SSB_W[2]),yaxs='i')
for(i in 1:nOMs)lines(yrs,SSB_W[[i]],col=cols[i],lty=ltys[i],lwd=2)
mtext("West stock SSB",3,line=1,font=2)

legend('topright',legend=LHs[,1],cex=1,text.col=cols,lty=ltys,col=cols,text.font=2,bty='n')

plot(yrs,SSB_E[[1]],col="white",ylim=c(0,ylim_SSB_E[2]),yaxs='i')
for(i in 1:nOMs)lines(yrs,SSB_E[[i]],col=cols[i],lty=ltys[i],lwd=2)
mtext("East stock SSB",3,line=1,font=2)

#plot(yrs,D_W[[1]],col="white",ylim=c(0,ylim_D_W[2]),yaxs='i')
#for(i in 1:nOMs)lines(yrs,D_W[[i]],col=cols[i],lty=ltys[i],lwd=2)
#mtext("West stock SSB trend",3,line=1,font=2)

#plot(yrs,D_E[[1]],col="white",ylim=c(0,ylim_D_E[2]),yaxs='i')
#for(i in 1:nOMs)lines(yrs,D_E[[i]],col=cols[i],lty=ltys[i],lwd=2)
#mtext("East stock SSB trend",3,line=1,font=2)


```


Figure 2. Stock-specific spawning biomass in kilo tonnes (top row) and relative to 1952 (bottom row)



# Stock mixing 

```{r mxing, fig.width=8.5, fig.height=9,echo=FALSE}


ylim_E_E<-range(lapply(F_E_E,range))
ylim_E_W<-range(lapply(F_E_W,range))
ylim_W_E<-range(lapply(F_W_E,range))
ylim_W_W<-range(lapply(F_W_W,range))
ylim_EinW<-range(lapply(F_EinW,range))
ylim_WinE<-range(lapply(F_WinE,range))

yrs<-OMIs[[1]]@years[1]:OMIs[[1]]@years[2]
par(mfrow=c(2,2),mai=c(0.35,0.35,0.4,0.01),omi=c(0.4,0.4,0.05,0.05))

plot(yrs,F_EinW[[1]],col="white",ylim=c(0,ylim_EinW[2]),yaxs='i')
for(i in 1:nOMs)lines(yrs,F_EinW[[i]],col=cols[i],lty=ltys[i],lwd=2)
mtext("Eastern stock in the West area",3,line=1,font=2)

plot(yrs,F_WinE[[1]],col="white",ylim=c(0,ylim_WinE[2]),yaxs='i')
for(i in 1:nOMs)lines(yrs,F_WinE[[i]],col=cols[i],lty=ltys[i],lwd=2)
mtext("Western stock in the East area",3,line=1,font=2)


plot(yrs,F_E_W[[1]],col="white",ylim=c(0,ylim_E_W[2]),yaxs='i')
for(i in 1:nOMs)lines(yrs,F_E_W[[i]],col=cols[i],lty=ltys[i],lwd=2)
mtext("Western area biomass that is Eastern",3,line=1,font=2)

plot(yrs,F_W_E[[1]],col="white",ylim=c(0,ylim_W_E[2]),yaxs='i')
for(i in 1:nOMs)lines(yrs,F_W_E[[i]],col=cols[i],lty=ltys[i],lwd=2)
mtext("Eastern area biomass that is Western",3,line=1,font=2)

legend('topright',legend=LHs[,1],cex=1,text.col=cols,lty=ltys,col=cols,text.font=2,bty='n')
mtext("Biomass fraction",2,line=0.5,font=2,outer=T)
mtext("Year",1,line=0.5,font=2,outer=T)

```

Figure 3. Biomass fractions by stock (top row) and area (bottom row).  
