
---
title: "MSE report"
subtitle: "ABT-MSE preliminary standardized report"
author: "`r params$Author`"
date:  "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true 
    
---


<style type="text/css">

body{ /* Normal  */
   font-size: 16px;
}
td {  /* Table  */
   font-size: 16px;
}
title { /* title */
 font-size: 26px;
}
h1 { /* Header 1 */
 font-size: 24px;
 color: DarkBlue;
}
h2 { /* Header 2 */
 font-size: 21px;
 color: DarkBlue;
}
h3 { /* Header 3 */
 font-size: 19px;
 color: DarkBlue;
}
code.r{ /* Code block */
  font-size: 16px;
}
pre { /* Code block */
  font-size: 16px
}
</style>



```{r intro,echo=F,results='asis'}

if(!is.na(params$introtext)){
  
  cat('\n')
  cat("# Introduction")
  cat('\n')
  cat(params$introtext)
  cat('\n')
  
}


```    


# Overview of performance metrics

```{r metric_key,echo=F,results='asis',fig.width=9, fig.height=5}


Metric<-c("AvC30","C10","C20","C30","D10","D20","D30","LD","DNC","LDNC","POF","POS","PGK","AAVC") 
Reported_by<-c(rep("Area",4),rep("Stock",9),"Area")
Description<-c("Mean  catches over first 30 projected years",
               "Mean catches over the first 10 projected years",
               "Mean catches over projected years 11-20",
               "Mean catches over projected years 21-30",
               "SSB relative to dynamic B0 after 10 projected yrs",
               "SSB relative to dynamic B0 after 20 projected yrs",
               "SSB relative to dynamic B0 after 30 projected yrs",
               "Lowest SSB depletion over the 30 years for which the MP is applied",
               "SSB depletion after 30 years, relative to zero catch scenario",
               "Lowest SSB depletion over the 30 years for which the MP is applied, relative to zero catch scenario",
               "Probability of overfishing (F>FMSY) over the first 30 projected years",
               "Probability of overfished state (B<BMSY) over the first 30 projected years",
               "Probability of green Kobe (F>FMSY and B<BMSY) over the first 30 projected years",
               "Percentage average annual variability in catches over the first 30 projected years")

key<-data.frame(Metric,Reported_by,Description)

key %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"))


```


# Performance metrics tables

Note that catch related performance metrics are reported by East West area (delimited by 45 deg W) and biomass / depletion metrics are reported by stock (ie originating from the Med and Gulf of Mexico)



```{r metric_tabs,echo=F,results='asis',fig.width=9, fig.height=5}


perf<-getperf(params$MSE,rnd=2)

cat('\n')
cat("## East ")
cat('\n')

perf[[1]] %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"))


cat('\n')
cat("## West ")
cat('\n')

perf[[2]] %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"))




```

# Performance metrics figures


```{r metric_fig,echo=F,results='asis',fig.width=9, fig.height=11}


PPlot(params$MSE)


```


# Projections


```{r Proj,echo=F,results='asis',fig.width=9, fig.height=11}


plot(params$MSE)


```


# Notes

Please submit requests / bug reports etc to <t.carruthers@oceans.ubc.ca>

