
---
title: "`r OMI@Name`"
subtitle: "ABT-MSE Operating model fitting report"
author: "Tom Carruthers"
date:  "`r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
geometry: margin=0.4in
fontsize: 10.5
---

### Operating model scenario is:

`r OMI@OMfactors[[1]]`  
`r OMI@OMfactors[[2]]`   
`r OMI@OMfactors[[3]]`    

### Area definitions for operating model:

```{r plotareas,echo=F,message=F,warning=F,error=F,fig.width=3, fig.height=2.5}

par(mar=rep(0.01,4))
areaplot(OMI)

```

Figure 1. Area definitions for operating model 


\newpage

###  Fits to CPUE indices of relative abundance
```{r CPUE fits, fig.width=7, fig.height=6.5,echo=FALSE}

plab<-c(paste0("(",letters[1:26],")"),paste0("(",paste0(letters[1:26],letters[1:26]),")"),paste0("(",paste0(letters[1:26],letters[1:26],letters[1:26]),")"))

firstrow<-match(1:OMI@nCPUEq,OMI@CPUEobs[,4])
Fleetnos<-as.vector(OMI@CPUEobs[firstrow,5])
Seasons<-as.vector(OMI@CPUEobs[firstrow,2])
Areas<-OMI@areanams[as.vector(OMI@CPUEobs[firstrow,3])]

nrow<-ceiling(OMI@nCPUEq/3)
ncol<-ceiling(OMI@nCPUEq/nrow)

par(mfcol=c(nrow,ncol),mai=c(0.3,0.3,0.1,0.01),omi=c(0.3,0.3,0.1,0.05))

VBi<-out$VB/rep(apply(out$VB,4,mean),each=out$ny*out$ns*out$nr)

for(i in 1:OMI@nCPUEq){
  
  tempdat<-subset(OMI@CPUEobs,OMI@CPUEobs[,4]==i)  
  obs<-as.numeric(tempdat[,6])
  pred<-exp(out$lnqCPUE[i])*VBi[tempdat[,c(1,2,3,5)]]
  yrs<-as.numeric(tempdat[,1]+OMI@years[1]-1)
  plot(yrs,obs,pch=19,col="#99999995",ylim=c(0,max(obs,pred)),ylab="",xlab="")
  lines(yrs,pred,lwd=1.5,col="#0000ff95")
  legend('topleft',legend=OMI@CPUEnames[i],bty='n')
  legend('topright',legend=c(paste0("Quarter: ",Seasons[i]),
                             paste0("Area: ",Areas[i])),bty='n')
  mtext(plab[i],3,adj=0.02,line=0.09,cex=0.7)
  
}

mtext("Relative abundance",2,line=0.5,outer=T)
mtext("Year",1,line=1,outer=T)

```

Figure 2. Assessment CPUE index fits (blue line = predicted, grey dots = index)


### Predicted seasonal and spatial biomass of Atlantic bluefin tuna ###

```{r indexfit, fig.width=7, fig.height=9.5,echo=FALSE}

  ny<-out$ny
  np<-out$np
  ns<-out$ns
  nr<-out$nr
  nf<-out$nf
  nl<-out$nl
  
  yrs<-OMI@years[1]:OMI@years[2]

  pch<-19
  cex<-0.8
  lwd=1.5
  pcols<-c("Red","Blue","#00ff0080","#ffff0080")
  

  popnams=c("East","West")
  subyrnams=c("Jan-Mar","Apr-Jun","Jul-Sept","Oct-Dec")
  areanams=OMI@areanams
  
  B<-array(NA,dim(out$N))
  ind<-TEG(dim(out$N))
  indw<-ind[,c(2,4,1)]
  B[ind]<-out$N[ind]*out$wt_age[indw]

  RAIp<-apply(B,c(5,3,2),sum) # r s y
  RAIo<-out$RAI
  muRAIp<-mean(RAIp)
  RAIp<-RAIp/muRAIp
  RAIo<-RAIo/mean(RAIo) 

  RAIpP<-apply(B,c(5,3,2,1),sum) # r s y p
  RAIpP<-RAIpP/muRAIp

  par(mfcol=c(nr,ns),mai=c(0.05,0.15,0.01,0.01),omi=c(0.4,0.5,0.1,0.05))
  ylim=c(0,max(RAIp,na.rm=T))
  ys<-pretty(seq(ylim[1],ylim[2]*1.2,length.out=4))
  xs<-pretty(seq(yrs[1],yrs[ny],length.out=6))
 
  l<-1
  
  for(s in 1:ns){
  
    for(r in 1:nr){
    
      #plot(yrs,RAIo[r,s,],col="#99999980",pch=pch,ylim=ylim,axes=F)
      plot(yrs,RAIp[r,s,],col="purple",pch=pch,ylim=ylim,axes=F,lwd=2,type="l")
      for(p in 1:np){
        lines(yrs,RAIpP[r,s,,p],col=pcols[p],lwd=1.5)
      }
    
      if(r==nr)axis(1,xs,xs)
      if(r<nr)axis(1,xs,NA)
      if(s==1)axis(2,ys,ys)
      if(s<(ns+1))axis(2,ys,NA)
      if(s==1)mtext(areanams[r],2,line=2.75)
      if(r==1)mtext(subyrnams[s],3,line=-0.5)
      if(r==1&s==ns)legend('topright',legend=c("Total",popnams),text.font=2,text.col=c("purple",pcols[1:np]),bty='n')
      
      mtext(plab[l],3,adj=0.02,line=-1.5,cex=0.7)
      l=l+1
    }
  
  }

  mtext("Year",1,outer=T,line=2)
  #mtext("Predicted relative abundance of Atlantic bluefin",3,line=1.5,outer=T)
```

Figure 3. Predicted seasonal and spatial biomass of Atlantic bluefin tuna (Recent period). 


### Historical Spawning biomass ###


```{r allSSB, fig.width=7, fig.height=4,echo=FALSE}
opt<-SRopt(out,plot=F,quiet=F,years=c(-Inf,Inf),type="BH",R0p=out$muR*exp(out$lnHR1))

res<-MSY_FAST(FML=out$FL[out$ny,,,,], iALK=out$iALK[,out$ny,,], N=out$N[,out$ny,,,],
         wt_age=t(out$wt_age[out$ny,,]), M_age=out$M_age, mat_age=out$mat_age,
         R0s=out$muR, fixpars=opt$par1,SRtypes=rep("BH",2))


allSSB<-cbind(apply(out$hSSB,1:2,mean),apply(out$SSB,1:2,mean))
matplot(OMI@Hyears[1]:OMI@years[2],t(allSSB)/1E6,ylim=c(0,max(allSSB)/1E6),type='l',col="white",xlab="Year",ylab="SSB (1000 t)")
abline(v=(180:230)*10,col="#99999920")
abline(h=(0:20)*500,col="#99999920")
matplot(OMI@Hyears[1]:OMI@years[2],t(allSSB)/1E6,ylim=c(0,max(allSSB)/1E6),type='l',col=c("red","blue"),lty=c(1,1),add=T)

abline(h=(res$SSBMSY_SSB0*out$SSB0)/1E6,col=c("#ff000080","#0000ff80"),lty=c(2,2))
abline(h=out$SSB0/1E6,col=c("#ff000080","#0000ff80"),lty=c(1,1))
abline(v=mean(OMI@Hyears[2],OMI@years[1]),col="#99999950",lwd=2)
legend('topleft',legend=c("West","East"),text.col=c("blue","red"),bty='n')
legend('top',legend=c("Unfished","MSY"),lty=c(1,2),bty='n')
  
```

Figure 4. Predicted seasonal and spatial biomass of Atlantic bluefin tuna (Recent period). 

### SSB, recruitment and F comparison with 2014 assessment (by East/West area, not East/West stock) 

```{r 2014comp, fig.width=7, fig.height=3.5,echo=FALSE}
# M3 SSB calculation
#muSSB<-apply(out$SSB,1:2,mean) # by stock (below is by east-west area)
Nind<-TEG(dim(out$N))
SSB<-array(NA,dim(out$N))
SSB[Nind]<-out$N[Nind]*out$mat_age[Nind[,c(1,4)]]*out$wt_age[Nind[,c(2,4,1)]]
SSBsum<-apply(SSB,c(2,3,5),sum) # SSB by year and area in spawning season
SSBmu<-apply(SSBsum,c(1,3),mean)
#sum(SSBmu[55,])==sum(SSBsum[55,,])/4 # Debug test
muSSB<-array(NA,c(np,ny))
muSSB[1,]<-apply(SSBmu*rep(c(0,0,0,0,1,1,1,1,1,1),each=out$ny),1,sum)
muSSB[2,]<-apply(SSBmu*rep(c(1,1,1,1,0,0,0,0,0,0),each=out$ny),1,sum)

muSSBc<-apply(muSSB,2,sum)

#SSBmu<-apply(apply(SSB,c(1,2,4,5),mean),c(1,2,4),sum)
EWareas<-array(NA,c(out$np,out$ny,out$nr))
EWareas[1,,]<-rep(c(0,0,0,0,1,1,1,1,1,1),each=out$ny)
EWareas[2,,]<-rep(c(1,1,1,1,0,0,0,0,0,0),each=out$ny)
#muSSB<-apply(SSBmu*EWareas,1:2,sum)

# Harvest rate calculation

#C_all_fts<-array(apply(out$Cpred,1:3,sum),dim(out$Cpred))
#Ubf<-out$Cpred/(out$Cpred+out$VB)
#muU<-apply(Ubf,sum)/apply(out$Cpred,c(1,3),sum)

CatEWo<-array(NA,dim(out$Cpred))
CatEWo[as.matrix(out$Cobs[,1:4])]<-out$Cobs[,5]

CatEW<-array(rep(apply(out$Cpred,c(1,3),sum),each=out$np, out$np),dim(EWareas))*EWareas
BEW<-array(rep(apply(out$B,c(1,3),mean),each=out$np),dim(EWareas))*EWareas
#U<-apply(CatEW,1:2,sum)/(apply(BEW,1:2,sum)+apply(CatEW,1:2,sum))
U<-apply(CatEW,1:2,sum)/apply(BEW,1:2,sum)

#sind<-c("E","W")
snams<-c("East","West")
stocknames<-c("East","West","East+West combined")

#find<-c("F25","Fapc")
#F25<-timeF25(FML=out$FL, iALK=out$iALK, N=out$N,
#         wt_age=t(out$wt_age[out$ny,,]), M_age=out$M_age, mat_age=out$mat_age,
#         R0s=out$R0, hs=out$h)
Rec<-apply(out$N[,,out$spawns[1],1,],1:2,sum)*exp(out$M_age[,1])# got to add back in mortality from end of time step
Rec<-apply(Rec,2,sum)

yrs<-OMI@years[1]:OMI@years[2]

par(mfcol=c(2,3),mai=c(0.30,0.75,0.01,0.01),omi=c(0.05,0.4,0.3,0.05))

for(pp in out$np:1){
  
  # SSB 
  tdat<-subset(dat,dat$area==snams[pp])[,c(3,5)]
  names(tdat)<-c("Year","Val")
  tdat$Val<-tdat$Val/1000
  ylim<-c(0,max(muSSB[pp,]/1000,as.numeric(as.character(tdat$Val))))
  plot(yrs,muSSB[pp,]/1000,col='#ff000090',lwd=2,ylab="SSB(t)",type="l",ylim=ylim)
  lines(tdat$Year,as.numeric(as.character(tdat$Val)),col="#00ff0090",lwd=2)
  mtext(stocknames[pp],3,line=1)
  
  # U
  tdat<-subset(dat,dat$area==snams[pp])[,c(3,8)]
  names(tdat)<-c("Year","Val")
  ylim<-c(0,max(U[pp,],as.numeric(as.character(tdat$Val))))
  plot(yrs,U[pp,],col='#ff000090',lwd=2,ylab="Harvest rate",type="l",ylim=ylim)
  lines(tdat$Year,as.numeric(as.character(tdat$Val)),col="#00ff0090",lwd=2)
  
  # F trajectory
  #if(find[pp]=='U'){
  #  tdat<-subset(dat,dat$Type==find[pp]&dat$Stock==sind[pp])
  #  ylim<-c(0,max(Fap[pp,],as.numeric(as.character(tdat$Val))))
  #  plot(yrs,Fap[pp,],col='#ff000090',lwd=2,ylab="",type="l",ylim=ylim)
  #  lines(tdat$Year,as.numeric(as.character(tdat$Val)),col="#00ff0090",lwd=2)
  #}else if(find[pp]=="F25"){
  #  tdat<-subset(dat,dat$Type==find[pp]&dat$Stock==sind[pp])
  #  ylim<-c(0,max(F25[pp,],as.numeric(as.character(tdat$Val))))
  #  plot(yrs,F25[pp,],col='#ff000090',lwd=2,ylab="",type="l",ylim=ylim)
  #  lines(tdat$Year,as.numeric(as.character(tdat$Val)),col="#00ff0090",lwd=2)
  #}
 
  
}

# SSB combined
tdat<-dat[,c(3,5)]
names(tdat)<-c("Year","Val")
tdat<-aggregate(tdat$Val,by=list(tdat$Year),sum)
names(tdat)<-c("Year","Val")
ylim<-c(0,max(muSSBc,as.numeric(as.character(tdat$Val))))
plot(yrs,muSSBc,col='#ff000090',lwd=2,ylab="SSB(t)",type="l",ylim=ylim)
lines(tdat$Year,as.numeric(as.character(tdat$Val)),col="#00ff0090",lwd=2)

legend('topright',legend=c("M3 OM","2014 assessment"),text.col=c('red','green'),bty='n')
mtext(stocknames[3],3,line=1)


# Recruitment combined
tdat<-dat[,c(3,7)]
names(tdat)<-c("Year","Val")
tdat<-aggregate(tdat$Val,by=list(tdat$Year),sum)
names(tdat)<-c("Year","Val")
ylim<-c(0,max(Rec,as.numeric(as.character(tdat$Val))))
plot(yrs,Rec,col='#ff000090',lwd=2,ylab="Recruitment",type="l",ylim=ylim)
lines(tdat$Year,as.numeric(as.character(tdat$Val)),col="#00ff0090",lwd=2)

  
```

Figure 3.Regional comparisons (45deg W) with 2014 stock assessment. Note that annual estimates from the operating model are calculated from average of the seasonal predictions. Harvest rates from the operating model are based on total stock biomass not vulnerable biomass which is fleet specific (and hence may not be comparable with assessments).  

### Stock-recruitment relationships (R0 is unfished mean recruitment)

```{r Stock-recruitment, fig.width=5.5, fig.height=2.5,echo=FALSE}

 #opt<-SRopt(out,plot=T,quiet=F,years=c(-Inf,Inf),type="BH",R0p=out$muR)
 opt<-SRopt(out,plot=T,quiet=F,years=c(-Inf,Inf),type="BH",R0p=out$muR*exp(out$lnHR1))

```

Figure 4. Model predicted pairs of SSB and recruitment(with a fitted Bev Holt for illustration)

### MSY reference points (2013 for comparison with previous assessment)

Table 1. Reference points by stock.

```{r refpoints, results='asis',echo=FALSE,fig.width=5}

refyr<-2013-OMI@years[1]+1

Fap<-meanFs(FML=out$FL[refyr,,,,], iALK=out$iALK[,refyr,,], N=out$N[,refyr,,,],
         wt_age=t(out$wt_age[refyr,,]))

#Fap<-timeFs(FML=out$FL, iALK=out$iALK, N=out$N,
#         wt_age=t(out$wt_age[out$ny,,]))

F_FMSY<-apply(Fap,1,max)/res[,2]
SSB_SSB0<-apply(out$SSB[,refyr,],1,mean)/out$SSB0#res$SSBMSY
res<-cbind(res,F_FMSY,SSB_SSB0)
res[,c(2,3,6,7,8,9,10)]<-round(res[,c(2,3,6,7,8,9,10)],3)
res[,c(1,4,5)]<-round(res[,c(1,4,5)]/1000,0)
kable(res)
  
```



### 2014 Assessment MSY reference points (by East/West area)

Table 2. Where available, reference points from most recent assessments

```{r 2014refpoints, results='asis',echo=FALSE,fig.width=5}

# MSY FMSYap UMSY BMSY SSBMSY BMSY/B0 SSBMSY/B0 recMSY/R0 F_FMSY SSB_BMSY
res[1,]<-c("-","-","-","-","-","-","-","-",0.75,0.45)
res[2,]<-c(3056,0.23,"-","-",13268,"-","-","-","0.47-0.85","0.35-2.1")
kable(res)
  
```


### Current annual mean F-at-age profile, all fleets, seasons, areas 

```{r meanFs, fig.width=3.5, fig.height=2,echo=FALSE}
par(mai=c(0.05,0.15,0.01,0.01),omi=c(0.66,0.5,0.1,0.05))
Fprof<-meanFs(FML=out$FL[out$ny,,,,], iALK=out$iALK[,out$ny,,], N=out$N[,out$ny,,,],
         wt_age=t(out$wt_age[out$ny,,]))
matplot(t(Fprof),type='l',xlab="Age",ylab="F",lty=c(1,1),col='white')
abline(h=(0:100)/100,col="#99999940",lty=1)
matplot(t(Fprof),type='l',lty=c(1,1),add=T,col=c("#ff000090","#0000ff90"),lwd=2)

legend('right',legend=c("West","East"),bty='n',text.col=c("blue","red"))
mtext("Age",1,outer=T,line=2)
mtext("Total annual F",2,outer=T,line=1.5)
```

Figure 5. The current profile of F at age summed over all fleets. 

### Estimated size selectivity by fleet

```{r estimatedsels, fig.width=6.5, fig.height=4,echo=FALSE}
  fleetnams=c(OMI@Fleets$name,'OTH')
  nr<-out$nr
  nf<-out$nf
  nl<-out$nl
  fcols<-rep(c("#99999980","#ff000080","#00ff0080","#0000ff80","#80802080","#ff00ff80","#00ffff80"),2)
  ltys<-rep(c(1,2),each=7)
  
  par(mai=c(0.05,0.15,0.01,0.01),omi=c(0.66,0.5,0.1,0.05))
  
  plot(out$ml[c(1,nl)],c(0,1),col='white',lwd=2,type='l',lty=ltys[1])
  
  for(f in 1:nf){
    
    lines(out$ml,out$sel[f,],col=fcols[f],lwd=2,lty=ltys[f])
    
  }
  legend('topright',legend=fleetnams,cex=0.7,text.font=2,text.col=fcols[1:nf],bty='n',col=fcols[1:nf],lty=ltys[1:nf])
  
  mtext("Length (cm)",1,outer=T,line=2)
  mtext("Selectivity",2,outer=T,line=1.5)

```

Figure 6. 

### Estimated unfished movement and spatial distribution

```{r est_mov, fig.width=8, fig.height=1.6,echo=FALSE}
plot_mov_dist(out,OMI)

```

Figure 7. The implied asymptotic distribution of fish under unfished conditions (red-orange-green-white, more to less)

### Fit to aggregate catches ###

```{r catchaggfit, fig.width=8.5, fig.height=9,echo=FALSE}

  firstyr=OMI@years[1]
  fleetnams=c(OMI@Fleets$name,'ALL OTH')
  areanams=OMI@areanams
  fcols<-c("#99999980","#ff000080","#00ff0080","#0000ff80","#ffff0080")

  np<-out$np   
  ny<-out$ny
  ns<-out$ns
  nr<-out$nr
  nf<-out$nf
  na<-out$na
  nl<-out$nl
  
  yrs<-firstyr:(firstyr+ny-1)
  
  # Fit to catches --------------------------
  col1<-c("red","blue","green","orange","grey","pink","brown","yellow","black","purple")
  cols<-makeTransparent(col1,90)
  
  CobsA<-array(NA,c(ny,ns,nr,nf))
  CobsA[out$Cobs[,1:4]]<-out$Cobs[,5]
  Co<-CobsA/1000
  Cp<-out$Cpred/1000
 
  par(mfcol=c(2,2),mai=c(0.45,0.45,0.4,0.01),omi=c(0.9,0.3,0.4,0.05))
  
  # Total catch
  ylim=c(0,max(c(apply(Co,1,sum,na.rm=T),apply(Cp,1,sum,na.rm=T))))
  plot(yrs,apply(Co,1,sum,na.rm=T),ylab="Catch (t)",pch=19,ylim=ylim)
  lines(yrs,apply(Cp,1,sum,na.rm=T),col="#ff000090")
  mtext("Total catch, all fleets, stocks, areas, seasons",3,line=0.6)
  
  # By area
  ylim<-c(0,max(apply(Co,c(1,3),sum,na.rm=T),apply(Cp,c(1,3),sum,na.rm=T)))
  matplot(yrs,apply(Co,c(1,3),sum,na.rm=T),pch=19,col=cols,ylim=ylim,ylab="Catch (t)")
  matplot(yrs,apply(Cp,c(1,3),sum,na.rm=T),type="l",add=T,col=cols,lty=1)
  legend('topright',legend=OMI@areanams,text.col=col1,bty='n')
  mtext("Catch by area, all fleets, stocks, seasons",3,line=0.6)
 
  # By season
  ylim<-c(0,max(apply(Co,1:2,sum,na.rm=T),apply(Cp,1:2,sum,na.rm=T)))
  matplot(yrs,apply(Co,1:2,sum,na.rm=T),pch=19,ylim=ylim,col=cols)
  matplot(yrs,apply(Cp,1:2,sum,na.rm=T),type="l",add=T,col=cols)
  legend('topright',legend=1:4,text.col=col1,bty='n')
  mtext("Catch by quarter, all fleets, stocks, seasons",3,line=0.6)
 
  ylim<-c(0,max(apply(Cp,4,sum,na.rm=T),apply(Co,4,sum,na.rm=T)))
  barplot(apply(Cp,4,sum,na.rm=T),names.arg=c(OMI@Fleets$name,"OTH"),border=NA,ylim=ylim,las=3)
  barplot(apply(Co,4,sum,na.rm=T),add=T)
  legend('topright',legend=c("Observed","Predicted"),fill=c("white","grey"),border=c("black","grey"),bty='n')
  mtext("Catch by fleet, all fleets, stocks, seasons",3,line=0.6)
 
  mtext("Catch (t)",2,line=0.4,outer=T)
  
  
```

Figure 8. Fit to a observed total catches aggregated over various axes (lines = predicted, points = observed)


### Fit to aggregate length composition ###

```{r fit to agg length observations, fig.width=7.5, fig.height=9,echo=FALSE}

  cexmult<-0.75
  maxcex<-1.5

  CLobsA<-array(NA,c(ny,ns,nr,nf,nl))
  CLobsA[out$CLobs[,1:5]]<-out$CLobs[,6]
  
  CLo<-apply(CLobsA,c(1,4,5),sum,na.rm=T)
  CLo[CLo==0]<-NA
  CLotot<-array(apply(CLo,1:2,sum,na.rm=T),dim(CLo))
  CLo<-CLo/CLotot
  CLp<-apply(out$CLtotpred,c(1,4,5),sum,na.rm=T)#*CLotot
  CLp<-CLp/array(apply(CLp,1:2,sum,na.rm=T),dim(CLp))
  
  PR<-(CLo-CLp)/(CLp*(CLotot-CLp)/CLotot)^0.5
  PR<-(CLo-CLp)/CLp^0.5
  PR<-(CLo-CLp)/CLp
  
  cexy<-abs(PR*cexmult)^0.5
  pchy<-array(1,dim=dim(cexy))
  pchy[PR<0]<-19
  coly<-array('blue',dim=dim(cexy))
  coly[PR<0]<-'red'
  
  CLoa<-apply(CLo,2:3,sum,na.rm=T)/apply(CLo,2,sum,na.rm=T)
  CLpa<-apply(CLp,2:3,sum,na.rm=T)/apply(CLp,2,sum,na.rm=T)

  # calculate unfished composition ==============
  Nrel<-t(exp(-apply(out$M_age,1,cumsum)))
  UFfreq<-array(NA,c(np,nf,nl))
  for(pp in 1:np){
    Lf<-apply(Nrel[pp,]*out$iALK[pp,1,,],2,sum)
    for(f in 1:nf){
      temp<-out$sel[f,]*Lf
      UFfreq[pp,f,]<-temp/sum(temp)
    }
    
  }
  
  
  #par(mfcol=c(7,2),mai=c(0.3,0.3,0.01,0.01),omi=c(0.3,0.3,0.1,0.05))
   par(mai=c(0.3,0.3,0.01,0.01),omi=c(0.3,0.3,0.1,0.05))
  dmat<-array(c((1:7)*2-1,(1:7)*2-1,1:7*2),c(7,3))
  layout(dmat)
  for(ff in 1:7){
    #if(ff==9)par(mfcol=c(ceiling((nf-8)/2),2),mai=c(0.3,0.3,0.01,0.01),omi=c(0.3,0.3,0.1,0.05))
    yrng<-range(out$CLobs[out$CLobs[,4]==ff,1],na.rm=T)
    yind<-yrng[1]:yrng[2]
    yrs<-yind+OMI@years[1]-1
    cex0<-cexy[yind,ff,]
    pch0<-pchy[yind,ff,]
    col0<-coly[yind,ff,]
    cex0[cex0>maxcex]<-maxcex
    xs<-rep(yrs,OMI@nl)
    ys<-rep(1:OMI@nl,each=length(yrs))
    plot(xs,ys,cex=cex0,pch=pch0,col=col0,axes=F,xlab="Year",ylab="Length (cm)")
    axis(1)
    axis(2,1:OMI@nl,OMI@mulen)
    legend('topleft',legend=OMI@Fleets$name[ff],bty='n')
    
    ylim=c(0,max(CLoa[ff,],CLpa[ff,],UFfreq[,ff,]))
    barplot(CLoa[ff,],ylim=ylim,names.arg=out$ml,border=NA,col='orange')
      
    lines(CLpa[ff,],col="#0000ff90",lwd=2)
    lines(UFfreq[1,ff,],col="#99999990",lwd=2)
    lines(UFfreq[2,ff,],col="#99999990",lwd=2,lty=2)
    #legend('topright',legend=paste("n=",round(sum(CLobsA[,,,ff,],na.rm=T)/1000,1),"k",sep=""),bty='n',cex=0.9)
    abline(v=xs,col="#99999980")
    #legend('topright',legend=paste("n=",round(sum(exp(apply(CLobsA[,,,ff,],1,sum)),na.rm=T)/1000,1),"k",sep=""),bty='n',cex=0.9)
  
  }
 
``` 

Figure 9a.Length composition residuals. Red points are negative Pearson residuals (predicted is higher than observed), blue circles are positive (predicted is lower than observed). Orange bars are observed, blue lines are model predicttions. 

```{r fit to agg length observations2, fig.width=7.5, fig.height=9,echo=FALSE}

 
  par(mai=c(0.3,0.3,0.01,0.01),omi=c(0.3,0.3,0.1,0.05))
  dmat<-array(c((1:7)*2-1,(1:7)*2-1,1:7*2),c(7,3))
  layout(dmat)
  for(ff in 8:nf){
    #if(ff==9)par(mfcol=c(ceiling((nf-8)/2),2),mai=c(0.3,0.3,0.01,0.01),omi=c(0.3,0.3,0.1,0.05))
    yrng<-range(out$CLobs[out$CLobs[,4]==ff,1],na.rm=T)
    yind<-yrng[1]:yrng[2]
    yrs<-yind+OMI@years[1]-1
    cex0<-cexy[yind,ff,]
    pch0<-pchy[yind,ff,]
    col0<-coly[yind,ff,]
    cex0[cex0>maxcex]<-maxcex
    xs<-rep(yrs,OMI@nl)
    ys<-rep(1:OMI@nl,each=length(yrs))
    plot(xs,ys,cex=cex0,pch=pch0,col=col0,axes=F,xlab="Year",ylab="Length (cm)")
    axis(1)
    axis(2,1:OMI@nl,OMI@mulen)
    legend('topleft',legend=OMI@Fleets$name[ff],bty='n')
    
    ylim=c(0,max(CLoa[ff,],CLpa[ff,],UFfreq[,ff,]))
    barplot(CLoa[ff,],ylim=ylim,names.arg=out$ml,border=NA,col='orange')
      
    lines(CLpa[ff,],col="#0000ff90",lwd=2)
    lines(UFfreq[1,ff,],col="#99999990",lwd=2)
    lines(UFfreq[2,ff,],col="#99999990",lwd=2,lty=2)
    #legend('topright',legend=paste("n=",round(sum(CLobsA[,,,ff,],na.rm=T)/1000,1),"k",sep=""),bty='n',cex=0.9)
    abline(v=xs,col="#99999980")
  
  }
 
``` 

Figure 9b.Length composition residuals. Red points are negative Pearson residuals (predicted is higher than observed), blue circles are positive (predicted is lower than observed).Orange bars are observed, blue lines are model predicttions.


## Other model estimates and fits ##

### Statistical properties of indices for use in Management Procedures

```{r stat_prop, results='asis',fig.width=7, fig.height=3.5,echo=FALSE}
  indnam<-unique(Obs@MPind$Name)
  nind<-length(indnam)
  
  for(i in 1:nind){
    
    cat('\n')  
    cat("### Index fit and statistical properties for",as.character(indnam[i]),"\n") 
  
    id<-subset(Obs@MPind,Obs@MPind$Name==indnam[i] & Obs@MPind$Year>=OMI@years[1] & Obs@MPind$Year<=OMI@years[2])
    yrs<-id$Year-OMI@years[1]+1
    stk<-id$Stock[1]
    
    indfit(SSB=apply(out$SSB[stk,yrs,],1,mean),ind=id$Index,Year=yrs+OMI@years[1]-1,sim=F,plot=T)
    cat('\n')  

  }
  


```

Figure 10. 




