
---
title: "`r OMI@Name`"
subtitle: "ABT-MSE Operating model fitting report"
author: "Tom Carruthers"
date:  "`r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
geometry: margin=0.4in
fontsize: 10.5
---

### Operating model scenario is:

`r OMI@OMfactors[[1]]`  
`r OMI@OMfactors[[2]]`   
`r OMI@OMfactors[[3]]`    


### Fits to CPUE indices of relative abundance

```{r CPUE fits, fig.width=7, fig.height=7,echo=FALSE}

firstrow<-match(1:OMI@nCPUEq,OMI@CPUEobs[,4])
Fleetnos<-as.vector(OMI@CPUEobs[firstrow,5])
Seasons<-as.vector(OMI@CPUEobs[firstrow,2])
Areas<-OMI@areanams[as.vector(OMI@CPUEobs[firstrow,3])]

nrow<-ceiling(OMI@nCPUEq/2)
ncol<-ceiling(OMI@nCPUEq/nrow)

par(mfcol=c(nrow,ncol),mai=c(0.3,0.3,0.01,0.01),omi=c(0.3,0.3,0.1,0.05))

for(i in 1:OMI@nCPUEq){
  
  tempdat<-subset(OMI@CPUEobs,OMI@CPUEobs[,4]==i)  
  obs<-tempdat[,6]
  pred<-exp(out$lnqCPUE[i])*out$VB[tempdat[,c(1,2,3,5)]]
  yrs<-tempdat[,1]+OMI@years[1]-1
  plot(yrs,obs,pch=19,col="#99999995",ylim=c(0,max(obs,pred)),ylab="",xlab="")
  lines(yrs,pred,lwd=1.5,col="#0000ff95")
  legend('topleft',legend=OMI@CPUEnames[i],bty='n')
  legend('topright',legend=c(paste0("Quarter: ",Seasons[i]),
                             paste0("Area: ",Areas[i])),bty='n')
  
}

mtext("Relative abundance",2,line=0.5,outer=T)
mtext("Year",1,line=1,outer=T)

```


### Fit to master abundance indices (standardized effort, partial Fs) ###

```{r indexfit, fig.width=7, fig.height=9.5,echo=FALSE}

  ny<-out$ny
  np<-out$np
  ns<-out$ns
  nr<-out$nr
  nf<-out$nf
  nl<-out$nl
  
  yrs<-OMI@years[1]:OMI@years[2]

  pch<-19
  cex<-0.8
  lwd=1.5
  pcols<-c("#ff000080","#0000ff80","#00ff0080","#ffff0080")
  

  popnams=c("East","West")
  subyrnams=c("Jan-Mar","Apr-Jun","Jul-Sept","Oct-Dec")
  areanams=OMI@areanams
  
  B<-array(NA,dim(out$N))
  ind<-TEG(dim(out$N))
  indw<-ind[,c(2,4,1)]
  B[ind]<-out$N[ind]*out$wt_age[indw]

  RAIp<-apply(B,c(5,3,2),sum) # r s y
  RAIo<-out$RAI
  muRAIp<-mean(RAIp)
  RAIp<-RAIp/muRAIp
  RAIo<-RAIo/mean(RAIo) 

  RAIpP<-apply(B,c(5,3,2,1),sum) # r s y p
  RAIpP<-RAIpP/muRAIp

  par(mfcol=c(nr,ns),mai=c(0.05,0.15,0.01,0.01),omi=c(0.4,0.5,0.4,0.05))
  ylim=c(0,max(RAIo,RAIp,na.rm=T))
  ys<-pretty(seq(ylim[1],ylim[2]*1.2,length.out=4))
  xs<-pretty(seq(yrs[1],yrs[ny],length.out=6))
 
  for(s in 1:ns){
  
    for(r in 1:nr){
    
      plot(yrs,RAIo[r,s,],col="#99999980",pch=pch,ylim=ylim,axes=F)
      lines(yrs,RAIp[r,s,],col="#ff00ff80",lwd=2)
      for(p in 1:np){
        lines(yrs,RAIpP[r,s,,p],col=pcols[p],lwd=1.5)
      }
    
      if(r==nr)axis(1,xs,xs)
      if(r<nr)axis(1,xs,NA)
      if(s==1)axis(2,ys,ys)
      if(s<(ns+1))axis(2,ys,NA)
      if(s==1)mtext(areanams[r],2,line=2.75)
      if(r==1)mtext(subyrnams[s],3,line=-0.5)
      if(r==1&s==ns)legend('topright',legend=popnams,text.font=2,text.col=pcols[1:np],bty='n')
    
    }
  
  }

  mtext("Year",1,outer=T,line=2)
  mtext("Predicted (line) versus observed (point) relative abundance of Atlantic bluefin",3,line=1.5,outer=T)
```
  
  
### SSB, recruitment and F comparison with 2014 assessment (by East/West area, not East/West stock) 

```{r 2014comp, fig.width=7, fig.height=3.5,echo=FALSE}
# M3 SSB calculation
#muSSB<-apply(out$SSB,1:2,mean) # by stock (below is by east-west area)
Nind<-TEG(dim(out$N))
SSB<-array(NA,dim(out$N))
SSB[Nind]<-out$N[Nind]*out$mat_age[Nind[,c(1,4)]]*out$wt_age[Nind[,c(2,4,1)]]
SSBsum<-apply(SSB[,,,,],c(2,3,5),sum) # SSB by year and area in spawning season
SSBmu<-apply(SSBsum,c(1,3),mean)
#sum(SSBmu[55,])==sum(SSBsum[55,,])/4 # Debug test
muSSB<-array(NA,c(np,ny))
muSSB[1,]<-apply(SSBmu*rep(c(0,0,0,0,1,1,1,1,1,1),each=out$ny),1,sum)
muSSB[2,]<-apply(SSBmu*rep(c(1,1,1,1,0,0,0,0,0,0),each=out$ny),1,sum)

#SSBmu<-apply(apply(SSB,c(1,2,4,5),mean),c(1,2,4),sum)
EWareas<-array(NA,c(out$np,out$ny,out$nr))
EWareas[1,,]<-rep(c(0,0,0,0,1,1,1,1,1,1),each=out$ny)
EWareas[2,,]<-rep(c(1,1,1,1,0,0,0,0,0,0),each=out$ny)
#muSSB<-apply(SSBmu*EWareas,1:2,sum)
muSSBc<-apply(muSSB,2,sum)


# Harvest rate calculation
CatEW<-array(rep(apply(out$Cpred,c(1,3),sum),out$np),dim(EWareas))*EWareas
BEW<-array(rep(apply(out$B,c(1,3),mean),out$np),dim(EWareas))*EWareas
U<-apply(CatEW,1:2,sum)/(apply(BEW,1:2,sum)+apply(CatEW,1:2,sum))



#sind<-c("E","W")
snams<-c("East","West")
stocknames<-c("East","West","East+West combined")

#find<-c("F25","Fapc")
#F25<-timeF25(FML=out$FL, iALK=out$iALK, N=out$N,
#         wt_age=t(out$wt_age[out$ny,,]), M_age=out$M_age, mat_age=out$mat_age,
#         R0s=out$R0, hs=out$h)
Rec<-apply(out$N[,,out$spawns[1],1,],1:2,sum)*exp(out$M_age[,1])# got to add back in mortality from end of time step
Rec<-apply(Rec,2,sum)

yrs<-OMI@years[1]:OMI@years[2]

par(mfcol=c(2,3),mai=c(0.30,0.75,0.01,0.01),omi=c(0.05,0.4,0.3,0.05))

for(pp in out$np:1){
  
  # SSB 
  tdat<-subset(dat,dat$area==snams[pp])[,c(3,5)]
  names(tdat)<-c("Year","Val")
  tdat$Val<-tdat$Val/1000
  ylim<-c(0,max(muSSB[pp,]/1000,as.numeric(as.character(tdat$Val))))
  plot(yrs,muSSB[pp,]/1000,col='#ff000090',lwd=2,ylab="SSB(t)",type="l",ylim=ylim)
  lines(tdat$Year,as.numeric(as.character(tdat$Val)),col="#00ff0090",lwd=2)
  mtext(stocknames[pp],3,line=1)
  
  # U
  tdat<-subset(dat,dat$area==snams[pp])[,c(3,8)]
  names(tdat)<-c("Year","Val")
  ylim<-c(0,max(U[pp,],as.numeric(as.character(tdat$Val))))
  plot(yrs,U[pp,],col='#ff000090',lwd=2,ylab="Harvest rate",type="l",ylim=ylim)
  lines(tdat$Year,as.numeric(as.character(tdat$Val)),col="#00ff0090",lwd=2)
  
  # F trajectory
  #if(find[pp]=='U'){
  #  tdat<-subset(dat,dat$Type==find[pp]&dat$Stock==sind[pp])
  #  ylim<-c(0,max(Fap[pp,],as.numeric(as.character(tdat$Val))))
  #  plot(yrs,Fap[pp,],col='#ff000090',lwd=2,ylab="",type="l",ylim=ylim)
  #  lines(tdat$Year,as.numeric(as.character(tdat$Val)),col="#00ff0090",lwd=2)
  #}else if(find[pp]=="F25"){
  #  tdat<-subset(dat,dat$Type==find[pp]&dat$Stock==sind[pp])
  #  ylim<-c(0,max(F25[pp,],as.numeric(as.character(tdat$Val))))
  #  plot(yrs,F25[pp,],col='#ff000090',lwd=2,ylab="",type="l",ylim=ylim)
  #  lines(tdat$Year,as.numeric(as.character(tdat$Val)),col="#00ff0090",lwd=2)
  #}
 
  
}

# SSB combined
tdat<-dat[,c(3,5)]
names(tdat)<-c("Year","Val")
tdat<-aggregate(tdat$Val,by=list(tdat$Year),sum)
names(tdat)<-c("Year","Val")
ylim<-c(0,max(muSSBc,as.numeric(as.character(tdat$Val))))
plot(yrs,muSSBc,col='#ff000090',lwd=2,ylab="SSB(t)",type="l",ylim=ylim)
lines(tdat$Year,as.numeric(as.character(tdat$Val)),col="#00ff0090",lwd=2)

legend('topright',legend=c("M3 OM","2014 assessment"),text.col=c('red','green'),bty='n')
mtext(stocknames[3],3,line=1)


# Recruitment combined
tdat<-dat[,c(3,7)]
names(tdat)<-c("Year","Val")
tdat<-aggregate(tdat$Val,by=list(tdat$Year),sum)
names(tdat)<-c("Year","Val")
ylim<-c(0,max(Rec,as.numeric(as.character(tdat$Val))))
plot(yrs,Rec,col='#ff000090',lwd=2,ylab="Recruitment",type="l",ylim=ylim)
lines(tdat$Year,as.numeric(as.character(tdat$Val)),col="#00ff0090",lwd=2)

  
```

### Stock-recruitment relationships (by East/West stock)
```{r Stock-recruitment, fig.width=5.5, fig.height=2.5,echo=FALSE}

 opt<-SRopt(out,plot=T,quiet=F,years=c(-Inf,Inf),type="BH",just_R0=FALSE,h=NA)


```

### MSY reference points (by East/West stock)

```{r refpoints, results='asis',echo=FALSE,fig.width=5}

res<-MSY_FAST(FML=out$FL[out$ny,,,,], iALK=out$iALK[,out$ny,,], N=out$N[,out$ny,,,],
         wt_age=t(out$wt_age[out$ny,,]), M_age=out$M_age, mat_age=out$mat_age,
         R0s=exp(opt$lnR0), fixpars=opt$par1,SRtypes=rep("BH",2))

refyr<-2013-OMI@years+1

Fap<-timeFs(FML=out$FL, iALK=out$iALK, N=out$N,
         wt_age=t(out$wt_age[out$ny,,]), M_age=out$M_age, mat_age=out$mat_age,
         R0s=out$muR, hs=out$h)

F_FMSY<-Fap[,refyr]/res[,2]
SSB_SSBMSY<-(apply(out$SSB,1:2,mean)/res$SSBMSY)[,refyr]
res<-cbind(res,F_FMSY,SSB_SSBMSY)
res[,c(2,3,6,7,8,9,10)]<-round(res[,c(2,3,6,7,8,9,10)],3)
res[,c(1,4,5)]<-round(res[,c(1,4,5)]/1000,0)
kable(res)
  
```


### 2014 Assessment MSY reference points (by East/West area)

```{r 2014refpoints, results='asis',echo=FALSE,fig.width=5}

# MSY FMSYap UMSY BMSY SSBMSY BMSY/B0 SSBMSY/B0 recMSY/R0 F_FMSY SSB_BMSY
res[1,]<-c("-","-","-","-","-","-","-","-",0.75,0.45)
res[2,]<-c(3056,0.23,"-","-",13268,"-","-","-","0.47-0.85","0.35-2.1")
kable(res)
  
```


### Current annual mean F-at-age profile, all fleets, seasons, areas 

```{r meanFs, fig.width=3.5, fig.height=2,echo=FALSE}
par(mai=c(0.05,0.15,0.01,0.01),omi=c(0.66,0.5,0.1,0.05))
meanFs(FML=out$FL[out$ny,,,,], iALK=out$iALK[,out$ny,,], N=out$N[,out$ny,,,],
         wt_age=t(out$wt_age[out$ny,,]), M_age=out$M_age, mat_age=out$mat_age,
         R0s=out$muR, hs=out$h)
mtext("Age",1,outer=T,line=2)
mtext("Total annual F",2,outer=T,line=1.5)
```


### Estimated size selectivity by fleet

```{r estimatedsels, fig.width=3.5, fig.height=2,echo=FALSE}
  fleetnams=c(OMI@Fleets$name,'OTH')
  nr<-out$nr
  nf<-out$nf
  nl<-out$nl
  fcols<-rep(c("#99999980","#ff000080","#00ff0080","#0000ff80","#ffff0080","#ff00ff80","#00ffff80"),2)
  ltys<-rep(c(1,2),each=7)
  
  par(mai=c(0.05,0.15,0.01,0.01),omi=c(0.66,0.5,0.1,0.05))
  
  plot(out$ml[c(1,nl)],c(0,1),col='white',lwd=2,type='l',lty=ltys[1])
  
  for(f in 1:nf){
    
    lines(out$ml,out$sel[f,],col=fcols[f],lwd=2,lty=ltys[f])
    
  }
  legend('topright',legend=fleetnams,text.font=2,text.col=fcols[1:nf],bty='n',col=fcols[1:nf],lty=ltys[1:nf])
  
  mtext("Length (cm)",1,outer=T,line=2)
  mtext("Selectivity",2,outer=T,line=1.5)

```


### Estimated unfished movement and spatial distribution

```{r est_mov, fig.width=8, fig.height=1.6,echo=FALSE}
plot_mov_dist(out,OMI)

```


### Fit to aggregate catches ###

```{r catchaggfit, fig.width=7, fig.height=10,echo=FALSE}

  firstyr=OMI@years[1]
  fleetnams=c(OMI@Fleets$name,'ALL OTH')
  areanams=OMI@areanams
  fcols<-c("#99999980","#ff000080","#00ff0080","#0000ff80","#ffff0080")

  np<-out$np   
  ny<-out$ny
  ns<-out$ns
  nr<-out$nr
  nf<-out$nf
  na<-out$na
  nl<-out$nl
  
  yrs<-firstyr:(firstyr+ny-1)
  
  # Fit to catches --------------------------
  col1<-c("red","blue","green","orange","grey","pink","brown","yellow","black","purple")
  cols<-makeTransparent(col1,90)
  
  CobsA<-array(NA,c(ny,ns,nr,nf))
  CobsA[out$Cobs[,1:4]]<-out$Cobs[,5]
  Co<-CobsA/1000
  Cp<-out$Cpred/1000
 
  par(mfcol=c(2,2),mai=c(0.45,0.45,0.4,0.01),omi=c(0.9,0.3,0.4,0.05))
  
  # Total catch
  ylim=c(0,max(c(apply(Co,1,sum,na.rm=T),apply(Cp,1,sum,na.rm=T))))
  plot(yrs,apply(Co,1,sum,na.rm=T),ylab="Catch (t)",pch=19,ylim=ylim)
  lines(yrs,apply(Cp,1,sum,na.rm=T),col="#ff000090")
  mtext("Total catch, all fleets, stocks, areas, seasons",3,line=0.6)
  
  # By area
  ylim<-c(0,max(apply(Co,c(1,3),sum,na.rm=T),apply(Cp,c(1,3),sum,na.rm=T)))
  matplot(yrs,apply(Co,c(1,3),sum,na.rm=T),pch=19,col=cols,ylim=ylim,ylab="Catch (t)")
  matplot(yrs,apply(Cp,c(1,3),sum,na.rm=T),type="l",add=T,col=cols,lty=1)
  legend('topright',legend=OMI@areanams,text.col=col1,bty='n')
  mtext("Catch by area, all fleets, stocks, seasons",3,line=0.6)
 
  # By season
  ylim<-c(0,max(apply(Co,1:2,sum,na.rm=T),apply(Cp,1:2,sum,na.rm=T)))
  matplot(yrs,apply(Co,1:2,sum,na.rm=T),pch=19,ylim=ylim,col=cols)
  matplot(yrs,apply(Cp,1:2,sum,na.rm=T),type="l",add=T,col=cols)
  legend('topright',legend=1:4,text.col=col1,bty='n')
  mtext("Catch by quarter, all fleets, stocks, seasons",3,line=0.6)
 
  ylim<-c(0,max(apply(Cp,4,sum,na.rm=T),apply(Co,4,sum,na.rm=T)))
  barplot(apply(Cp,4,sum,na.rm=T),names.arg=c(OMI@Fleets$name,"OTH"),border=NA,ylim=ylim,las=3)
  barplot(apply(Co,4,sum,na.rm=T),add=T)
  legend('topright',legend=c("Observed","Predicted"),fill=c("white","grey"),border=c("black","grey"),bty='n')
  mtext("Catch by fleet, all fleets, stocks, seasons",3,line=0.6)
 
  mtext("Catch (t)",2,line=0.4,outer=T)
  
  
```

### Fit to aggregate length composition ###

```{r fit to agg length observations, fig.width=7, fig.height=10,echo=FALSE}
  
 
  cexmult<-0.75
  maxcex<-1.5

  CLobsA<-array(NA,c(ny,ns,nr,nf,nl))
  CLobsA[out$CLobs[,1:5]]<-out$CLobs[,6]
  
  CLo<-apply(CLobsA,c(1,4,5),sum,na.rm=T)
  CLo[CLo==0]<-NA
  CLotot<-array(apply(CLo,1:2,sum,na.rm=T),dim(CLo))
  CLo<-CLo/CLotot
  CLp<-apply(out$CLtotpred,c(1,4,5),sum,na.rm=T)#*CLotot
  CLp<-CLp/array(apply(CLp,1:2,sum,na.rm=T),dim(CLp))
  
  PR<-(CLo-CLp)/(CLp*(CLotot-CLp)/CLotot)^0.5
  PR<-(CLo-CLp)/CLp^0.5
  PR<-(CLo-CLp)/CLp
  
  cexy<-abs(PR*cexmult)^0.5
  pchy<-array(1,dim=dim(cexy))
  pchy[PR<0]<-19
  coly<-array('red',dim=dim(cexy))
  coly[PR<0]<-'blue'
  
  par(mfcol=c(7,2),mai=c(0.3,0.3,0.01,0.01),omi=c(0.3,0.3,0.1,0.05))

  for(ff in 1:nf){
    #if(ff==9)par(mfcol=c(ceiling((nf-8)/2),2),mai=c(0.3,0.3,0.01,0.01),omi=c(0.3,0.3,0.1,0.05))
    yrng<-range(out$CLobs[out$CLobs[,4]==ff,1],na.rm=T)
    yind<-yrng[1]:yrng[2]
    yrs<-yind+OMI@years[1]-1
    cex0<-cexy[yind,ff,]
    pch0<-pchy[yind,ff,]
    col0<-coly[yind,ff,]
    cex0[cex0>maxcex]<-maxcex
    xs<-rep(yrs,OMI@nl)
    ys<-rep(1:OMI@nl,each=length(yrs))
    plot(xs,ys,cex=cex0,pch=pch0,col=col0)
    legend('topleft',legend=OMI@Fleets$name[ff],bty='n')
  
  }
  
  

 
  
    
``` 





## Other model estimates and fits ##

### Statistical properties of indices for use in Management Procedures

```{r stat_prop, results='asis',fig.width=7, fig.height=3.5,echo=FALSE}
  indnam<-unique(Obs@MPind$Name)
  nind<-length(indnam)
  for(i in 1:nind){
    
    cat('\n')  
    cat("### Index fit and statistical properties for",as.character(indnam[i]),"\n") 
  
    id<-subset(Obs@MPind,Obs@MPind$Name==indnam[i] & Obs@MPind$Year<(out$ny+1))
    yrs<-id$Year
    stk<-id$Stock[1]
    
    indfit(SSB=apply(out$SSB[stk,yrs,],1,mean),ind=id$Index,Year=yrs+1959,sim=F,plot=T)
    cat('\n')  

  }
  


```


### Fit to observed catches ###

```{r catchfit, results='asis',echo=FALSE}

  firstyr=1960
  fleetnams=c(OMI@Fleets$name,'ALL OTH')
  areanams=OMI@areanams
  subyrnams=c("Jan-Mar","Apr-Jun","Jul-Sept","Oct-Dec")
  
  pch<-19
  cex<-0.8
  lwd=2
  
  np<-out$np   
  ny<-out$ny
  ns<-out$ns
  nr<-out$nr
  nf<-out$nf
  na<-out$na
  nl<-out$nl
  
  yrs<-firstyr:(firstyr+ny-1)
  
  # Fit to catches --------------------------
  
  CobsA<-array(NA,c(ny,ns,nr,nf))
  CobsA[out$Cobs[,1:4]]<-out$Cobs[,5]
  Co<-CobsA/1000
  Cp<-out$Cpred/1000
  #Co<-log(Co)
  #Cp<-log(Cp)
  
  
  for(f in 1:nf){
    
    cat('\n')  
    cat("### Observed catches (tonnes) for ",fleetnams[f],"\n") 
    
    par(mfcol=c(nr,ns),mai=c(0.05,0.15,0.01,0.01),omi=c(0.4,0.5,0.15,0.05))
    ylim=c(0,max(Co[,,,f],Cp[,,,f],na.rm=T))
    ys<-pretty(seq(ylim[1],ylim[2]*1.2,length.out=4))
    xs<-pretty(seq(yrs[1],yrs[ny],length.out=6))
  
    for(s in 1:ns){
    
      for(r in 1:nr){
      
       plot(yrs,Co[,s,r,f],pch=pch,cex=cex,ylim=ylim,axes=F)
       lines(yrs,Cp[,s,r,f],col="#ff000099",lwd=lwd)
       if(r==nr)axis(1,xs,xs)
       if(r<nr)axis(1,xs,NA)
       if(s==1)axis(2,ys,ys)
       if(s<(ns+1))axis(2,ys,NA)
       if(s==1)mtext(areanams[r],2,line=2.75)
       if(r==1)mtext(subyrnams[s],3,line=-0.5)
       
       if(r==1&s==ns)legend('topright',legend=c("Obs","Pred"),text.col=c("black","red"),bty='n')
      
     }
    
   }
  
   mtext("Year",1,outer=T,line=2)
  # mtext("Predicted (line) versus observed (point) catches of Atlantic bluefin (log tonnes)",3,line=1.5,outer=T)
    cat('\n') 
 }
  
```



```{r fit to length observations, results='asis',echo=FALSE}
  
  ny<-out$ny
  ns<-out$ns
  nr<-out$nr
  nf<-out$nf
  nl<-out$nl

  CLobsA<-array(NA,c(ny,ns,nr,nf,nl))
  CLobsA[out$CLobs[,1:5]]<-out$CLobs[,6]
  
  CLo<-apply(CLobsA,c(1,4,5),sum,na.rm=T)
  CLo[CLo==0]<-NA
  CLotot<-array(apply(CLo,1:2,sum,na.rm=T),dim(CLo))
  CLo<-CLo/CLotot
  CLp<-apply(out$CLtotpred,c(1,4,5),sum,na.rm=T)#*CLotot
  CLp<-CLp/array(apply(CLp,1:2,sum,na.rm=T),dim(CLp))
  
  for(f in 1:nf){
    
    #jpeg(paste(outdir,"Catch_comp_fit_",fleetnams[f],".jpg",sep=""),res=300,height=7,width=8,units='in')
    cat('\n')  
    cat("### Length composition fit for",fleetnams[f],"\n") 
    
    yrswd<-unique(array(1:ny,dim(CLo[,f,]))[!is.na(CLo[,f,])])
    yrswd<-yrswd[order(yrswd)]
    nplotyrs<-length(yrswd)
    
    ncs<-6
    nrs<-ceiling(nplotyrs/ncs)
    
    par(mfrow=c(nrs,ncs),mai=c(0.15,0.25,0.01,0.01),omi=c(0.5,0.15,0.4,0.05))
    
    ylim=c(0,0.4)
    ys<-pretty(seq(ylim[1],ylim[2]*1.2,length.out=4))
    xs<-pretty(seq(1,out$nl,length.out=8))
    
    for(i in 1:nplotyrs){
      
      y<-yrswd[i]
      if(i>(nplotyrs-ncs)){
        barplot(CLo[y,f,],ylim=ylim,names.arg=out$ml,border=NA,col='orange')
      }else{
        barplot(CLo[y,f,],ylim=ylim,border=NA,col='orange')
      }
      lines(CLp[y,f,],col="#0000ff90",lwd=1.5)
      legend('topleft',legend=y+firstyr-1,bty='n',cex=0.9)  
      legend('topright',legend=paste("n=",round(sum(CLobsA[y,,,f,],na.rm=T)/1000,1),"k",sep=""),bty='n',cex=0.9)
      abline(v=xs,col="#99999980")
    }   
    
    
    mtext("Length (cm)",1,outer=T,line=2)
    mtext(paste("Predicted (line) versus observed (point) catch at length for the ",fleetnams[f]," fleet (n=",floor(sum(CLobsA[,,,f,],na.rm=T)/1000),"k)",sep=""),3,line=1.25,outer=T)
    
    #dev.off()
    cat('\n') 
  }  

#for (i in 1:2){
#cat('\n')  
#cat("#This is a heading for ", i, "\n") 
#hist(cars[,i])
#cat('\n') 
#}
```

